MSB1015_Assignment 2

### 2019-10-13 MSB1015_Assignment2_SuzannetenHage.Rmd
Improved documentation on section 2
Some description of which descriptors were used was missing, so this has been added.

In this project I use a SPARQL query to obtain the smiles and boiling points of simple alkanes from WikiData (ref2). I use the smiles to get descriptors from the CDK database (ref3-6). These descriptors contain information on the structural properties of the alkanes (see section 2 for more details). Finally, I train a Partial Least Squares (PLS) model to predict these properties from the chemical properties of the compounds and plot the results.

@@

**2. Get the descriptors of the alkane structures**
In this section, I get descriptors for all alkanes from CDK based on their smiles. These descriptors will be used later as predictors in the PLS model.

@@

#Determine which descriptors to get. 
descriptor_names <- c(
'org.openscience.cdk.qsar.descriptors.molecular.APolDescriptor',
'org.openscience.cdk.qsar.descriptors.molecular.WienerNumbersDescriptor',
'org.openscience.cdk.qsar.descriptors.molecular.MDEDescriptor',
'org.openscience.cdk.qsar.descriptors.molecular.FragmentComplexityDescriptor'
)

#Get descriptors
data_descriptors <- eval.desc(parsed_smiles, descriptor_names)

>>>>

In this project I use a SPARQL query to obtain the smiles and boiling points of simple alkanes from WikiData (ref2). I use the smiles to get descriptors from the chemical development kit (CDK) database (ref3-6). These descriptors contain information on the structural properties of the alkanes (see section 2 for more details). Finally, I train a Partial Least Squares (PLS) model to predict these properties from the chemical properties of the compounds and plot the results.

@@

**2. Get the descriptors of the alkane structures**
In this section, I use four descriptors for all alkanes from CDK. I can obtain the descriptors based on the alkane smiles. These descriptors will be used later as predictors in the PLS model.

*APolDescriptor:*
This describes the sum of the atomic polarizabilities.

*WienerNumbersDescriptor:*
This gives the Wiener numbers (see ref1). It returns the Wiener Path Number and the Wiener Polarity Number.

*MDEDescriptor:*
Returns the Molecular Distance Edge.

*FragmentComplexityDescriptor:*
Returns the complexity of a system.

@@

#Determine which descriptors are of interest. To add/remove descriptors, change this vector to include the desired descriptors. 
descriptor_names <- c(
'org.openscience.cdk.qsar.descriptors.molecular.APolDescriptor',
'org.openscience.cdk.qsar.descriptors.molecular.WienerNumbersDescriptor',
'org.openscience.cdk.qsar.descriptors.molecular.MDEDescriptor',
'org.openscience.cdk.qsar.descriptors.molecular.FragmentComplexityDescriptor'
)

#Get descriptor values form the CDK database. 
data_descriptors <- eval.desc(parsed_smiles, descriptor_names)

#At the time of writing, this returns a dataframe of 23 variables describing 134 alkanes. 
```
